A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-03-27 referee_response.txt

We wish to thank the referee for their supportive and helpful comments on our
manuscript "A VLT/FORS2 Narrowband Imaging Search for MgII Emission in
z~0.70 Galaxies".  We have implemented each of the suggestions they
sent in their report (in boldface type).  Please see our direct
responses to each comment below.

@@

Comment:"In the last paragraph of Section 2.1 a little more information about the absorption lines would be helpful. 
The velocities are quoted as ~150-420 km/s -- is this measured from the centroids of the lines? 
As the authors know, the velocity of MgII can be significantly affected by infilling from emission, so a bit 
more detail on where these numbers come from and how to interpret them would be useful. 
It would also be helpful to note that the equivalent widths given here are in the rest frame, since 
they are discussed in the observed frame in most of the rest of the paper."

Reply: We expanded the last paragraph of Section 2.1 to include a more
detailed description of the velocities being reported.  We also
added the velocity reported for each galaxy to Table 1. Additionally,
we now discuss the type of model that was used
to fit the lines and how this mitigates the effects of infilling from scattered
emission.  We have added a note stating that the EWs mentioned
here are rest-frame equivalent widths.

Comment: "Please add a note to Table 1 explaining what tau_V is, since it isn't discussed until later in the paper
and it is a bit less obvious than the other quantities in the table."

Reply: We have added a note to Table 1 which gives some description of tau_V.

Comment: "In the discussion of previous results in Section 6.1, I think providing some context from Henry et al 2018 would
be useful. Although this paper didn't present spatially extended emission, their results on which galaxies are 
likely to have strong MgII emission is relevant, in particular the finding that nebular emission is important as 
well as resonantly scattered continuum photons, and the finding that the strength of the emission may be set by the 
escape fraction of MgII photons rather than the intrinsic production."

Reply: We have added discussion of results from Henry et al (2018) to
a new section following Section 6.1 as requested (see Section 6.2).

### 2019-03-27 for_submission/rvaught_2018.tex
Kate's final edits

The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities, $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \added{The reported maximum outflow velocities, see Table \ref{tab:prop}, are the result of fitting a two-velocity component model to the absorption line profile. The two component model assumes that there is a systemic velocity and ``flow" velocity that both contribute to the overall line profile. The maximum outflow velocity is the velocity of the flow, $v_{\rm flow}$ minus a fitted doppler parameter, $b_{D,\rm flow}/\sqrt{2}$. The use of the two component model is helpful to mitigate the effects of scattered emission filling up the absorption line which in turn pushes the trough of the line blueward. It is assumed that the resonant emission will reduce the systemic velocity, leaving the flow velocity to characterize the outflow. The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}. Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

\begin{deluxetable*}{c c D D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object\tablenotemark{a}} &  \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} &\colhead{$\Delta v_{\rm max}$\tablenotemark{b}} &\multicolumn2c{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$\tablenotemark{c}} \\ 
\colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(km s$^{-1}$)} & \multicolumn2c{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   &   $-187_{-16}^{+12}$ & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ &   $-168_{-126}^{+33}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablenotetext{a}{\added{Galaxy ID's are named according to the object R.A and DEC. position.}}
\tablenotetext{b}{\added{Maximum outflow velocity, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$ where $b_{D,\rm flow}$ is the Doppler parameter or velocity width of the absorption.}}
\tablenotetext{c}{\added{Total V-band optical depth.}} 
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

@@

\section{Discussion}\label{sec:discussion}
\subsection{Previous Detection of extended \ion{Mg}{2} Emission}
Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}. In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a SFR of $49.8\msunperyr$. This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum. The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture. Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs. SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel). These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging. Taken at face value, the left panel of Figure \ref{fig:all_limits} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($\gtrsim50 \msunperyr$) exhibit brighter \ion{Mg}{2} emission.

\subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
\added{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. In addition to the observed trend that emission strength may be correlated with galaxy mass, recent studies by \cite{Henry2018} and \cite{Guseva2019} show significant contribution from nebular emission to the total \ion{Mg}{2} emission strength. In \cite{Henry2018} report strong \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies. Photoionization modeling of the observed strength of emission suggests that in addition to scattering of continuum photons, HII regions may also produce a non-negligible contribution to observed \ion{Mg}{2} emission, with the strength set b the escape fraction. In \cite{Guseva2019}, the authors find that low metallicity \ion{Mg}{2} emitters from \cite{Feltre2018} and \cite{Finley2017} have high H$\beta$ EW's, confirming that \ion{Mg}{2} emission has nebular origin. However, our sample of galaxies are comparitavely more massive and thus richer in metal than the galaxies that are known to contain significant nebular emission. The total contribution from nebular \ion{Mg}{2} to the total \ion{Mg}{2} emission remains to be determined for more massive and metal rich galaxies.}

Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected extended \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.

@@

\subsection{Geometry of Scattering Material}
In the context of the idealized models of cool gas outflows discussed in \cite{Prochaska_2011}, radiative transfer calculations predict that strong \ion{Mg}{2} emission will always accompany the blueshifted \ion{Mg}{2} absorption that is ubiquitously observed to trace galactic-scale winds \citep{Weiner2009,Martin2012,Rubin_2014}. For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted.  Therefore, the total equivalent width of both the absorption and emission features is equal to zero in such models. Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be generated by this wind, and how the SB of this emission compares to our detection limits.

>>>>

The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \added{These maximum outflow velocities (listed in Table \ref{tab:prop}) are determined from fitting a two-velocity component model to the absorption line profiles. The two-component model assumes that there is an absorption component due to stellar atmospheres and the interstellar medium with a velocity fixed at systemic, as well as a ``flow'' absorption component with a velocity that is allowed to float.  %that both contribute to the overall line profile.
The maximum outflow velocity $\Delta v_{\rm max}$ is the fitted central velocity of the flow component, $v_{\rm flow}$, minus the fitted Doppler parameter, $b_{D,\rm flow}/\sqrt{2}$.  It thus is indicative of the most extreme flow velocities traced by each absorption line profile.
The two-component model does not explicitly include a contribution to the line profile from scattered emission, which
can be significant at velocities close to systemic \citep{Prochaska_2011}.  However, as discussed in \cite{Rubin_2014}, it is expected that scattered emission will primarily tend to reduce the strength of the fitted systemic component, and will have a minor effect on fitted flow component velocities and line widths (see their Appendix C).
%The use of the two-component model mitigates the effect of scattered emission
%on the fitted velocity.
%filling up the absorption line which in turn pushes the trough of the line blueward. It is assumed that the resonant emission will reduce the systemic %velocity, leaving the flow velocity to characterize the outflow. 
%The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}
}

Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data, also performed by \cite{Rubin_2014}, yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. All of these sample properties as well as target coordinates %taken from \cite{Rubin_2014}, 
are listed in Table \ref{tab:prop}.

@@

\begin{deluxetable*}{c c D D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object\tablenotemark{a}} &  \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} &\colhead{$\Delta v_{\rm max}$\tablenotemark{b}} &\multicolumn2c{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$\tablenotemark{c}} \\ 
\colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(km s$^{-1}$)} & \multicolumn2c{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   &   $-187_{-16}^{+12}$ & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
J033231.36-274725.0 (J.36)     &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ &   $-168_{-126}^{+33}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
\enddata
%\tablenotetext{a}{\added{Galaxy names include their  are named according to the object R.A and DEC. position.}}
\tablenotetext{a}{\added{Galaxy names include their R.A. and Declination in the J2000.0 epoch.  The names in parentheses are used to identify each object throughout the paper.}}
\tablenotetext{b}{\added{Maximum outflow velocity traced by \ion{Mg}{2}, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$, where $b_{D,\rm flow}$ is the fitted Doppler parameter and $v_{\rm flow}$ is the fitted central velocity of the ``flow'' component in a two-component model of the absorption line profile.}}
\tablenotetext{c}{\added{Total $V$-band optical depth of dust attenuating light from the young stellar population in each galaxy as modeled by MAGPHYS.  This includes contributions from dust in both \ion{H}{2}  regions and the ambient ISM.} }
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

@@

\section{Discussion}\label{sec:discussion}
\subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}. In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a SFR of $49.8\msunperyr$. This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum. The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture. Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs. SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel). These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.

\subsection{Possible Correlation of \ion{Mg}{2} Emission Strength with Galaxy Properties }
{\bf Taken at face value, the left panel of Figure \ref{fig:all_limits} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. 
The constraints shown in the middle panel of Figure \ref{fig:all_limits} are similarly suggestive of (and consistent with) a negative correlation between the SB of extended \ion{Mg}{2} emission and galaxy stellar mass. 
Future observations are needed to verify these trends, and the possibility that objects with yet higher SFRs ($\gtrsim50 \msunperyr$) exhibit brighter extended \ion{Mg}{2} emission.  
Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected extended \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent and/or optical depth of wind material.
%Such a finding could be indicative of higher optical depth material extending to larger distances from more highly star-forming galaxies.
Here we note that a similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs. $M_*$. }

{\bf A potential complicating factor in the interpretation of trends in \ion{Mg}{2} SB with galaxy properties is the possible contribution of nebular emission to the \ion{Mg}{2} line profiles.
%In addition to this observed 
%anticorrelation,
%trend that emission strength may be correlated with galaxy mass,
Recent studies by \cite{Henry2018} and \cite{Guseva2019} suggest that there may be a significant contribution from nebular emission (i.e., from \ion{H}{2} regions) to the total \ion{Mg}{2} emission strength in some galaxies. 
In detail, \cite{Henry2018} report strong \ion{Mg}{2} emission having %escape fractions between $0-0.9$ 
$\rm EW_{2796}\sim 0.4-9.1$ \AA\ along with negligible absorption
arising in a sample of extreme compact starburst galaxies (``Green Peas'') at $z \sim 0.2-0.3$. 
Their photoionization modeling of the emission line strengths suggests that the observed 
\ion{Mg}{2} emission fluxes can in fact be 
dominated by \ion{H}{2} region emission in such low-metallicity systems (with $Z = 0.16-0.32 Z_{\odot}$).  They also note that higher metallicity and/or more dusty conditions will produce weaker nebular emission.  Moreover, these authors find that the strength of observed \ion{Mg}{2} emission is correlated with the escape fraction of \ion{Mg}{2} photons, suggesting that within their sample, galaxies with the weakest observed emission may have the strongest intrinsic nebular emission.   }

%in addition to scattering of continuum photons, HII regions may also produce a non-negligible contribution to observed \ion{Mg}{2} emission, with the strength set b the escape fraction. 
%In \cite{Guseva2019}, the authors find that low metallicity \ion{Mg}{2} emitters from \cite{Feltre2018} and \cite{Finley2017} have high H$\beta$ EW's, confirming that \ion{Mg}{2} emission has nebular origin. 
{\bf Given that our sample of galaxies exhibits quite weak emission in comparison to those studied by \citet{Henry2018}, at face value this latter finding suggests that they likely have \ion{H}{2} regions producing significant intrinsic \ion{Mg}{2} emission.
However, our sample (along with TKRS4389) is also $\gtrsim1$ dex higher in stellar mass and thus richer in both metals (by $\sim +0.9$ dex in $\log$ O/H; \citethnop{Zahid2011}) and dust than the \citet{Henry2018} Green Peas.
%the galaxies that are known to produce significant nebular emission. 
While there may indeed be a nebular contribution to \ion{Mg}{2} emission when it is observed in galaxies in this mass range,  
%The nebular contribution %from nebular \ion{Mg}{2} to the total 
more detailed photoionization modeling is required to estimate line luminosities for the relevant physical conditions.  As nebular emission is reprocessed by scattering just as continuum photons are, its presence would tend to brighten any spatially-extended line component, and any trends in nebular emission line strengths with $M_*$ or SFR would be reflected in the surface brightnesses of extended emission.
  The nebular contribution should therefore be considered by future studies interpreting the meaning of putative trends in extended line SB with galaxy properties.}
%\ion{Mg}{2} emission remains to be determined for more massive and metal rich galaxies.}
%SAY SOMETHING ABOUT HOW THIS IS SEPARATE / IRRELEVANT TO EXTENDED EMISSION STUDIES

@@

\subsection{Geometry of Scattering Material}
In the context of the idealized models of cool gas outflows discussed in \cite{Prochaska_2011}, radiative transfer calculations predict that strong \ion{Mg}{2} emission will always accompany the blueshifted \ion{Mg}{2} absorption that is ubiquitously observed to trace galactic-scale winds \citep{Weiner2009,Martin2012,Rubin_2014}. For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted.  Therefore, the total equivalent width of both the absorption and emission features is equal to zero in such models. Assuming that our galaxies host an isotropic and dust-free wind {\bf (and that they do not produce significant nebular \ion{Mg}{2} emission)}, we wish to determine how much emission is predicted to be generated by this wind, and how the SB of this emission compares to our detection limits.
